\documentclass[format=sigconf]{acmart}


% For formal tables
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{tabu}

% For subcaption
\captionsetup[subfigure]{labelformat=simple}
\renewcommand{\thesubfigure}{(\alph{subfigure})}


\begin{document}

% Conference Information
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{rightsretained}
\acmConference[GECCO '18 Companion]{Genetic and Evolutionary Computation Conference Companion}{July 15--19, 2018}{Kyoto, Japan}
\acmBooktitle{GECCO '18 Companion: Genetic and Evolutionary Computation Conference Companion, July 15--19, 2018, Kyoto, Japan}
\acmDOI{10.1145/3205651.3208770}
\acmISBN{978-1-4503-5764-7/18/07}

\title{Parameter Space Analysis of Genetic Algorithm Using Support Vector Regression}

\author{Hwi-Yeon Cho}
\affiliation{
  \institution{Dept. Comp. Sci., Kwangwoon Univ.}
  \country{Seoul, Republic of Korea}
}
\email{hwyn.cho@gmail.com}

\author{Hye-Jin Kim}
\affiliation{
  \institution{Dept. Comp. Sci., Kwangwoon Univ.}
  \country{Seoul, Republic of Korea}
}
\email{ovoa22@gmail.com}

\author{Yong-Hyuk Kim}
\affiliation{
  \institution{Dept. Comp. Sci., Kwangwoon Univ.}
  \country{Seoul, Republic of Korea}
}
\email{yhdfly@kw.ac.kr}


% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{H.-Y. Cho et al.}

\begin{abstract}
  Tuning various parameters coexisting in genetic algorithms (GAs) has a direct impact on the performance of GA. Because of this, finding a proper parameter value is challenging. In this study, we use support vector regression to show the appropriate parameter space of GA. Moreover, this was applied and analyzed to solving $NK$-landscape problems. As a result, we show the complexities and difficulties of GA parameter space through this paper.
\end{abstract}

% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
\begin{CCSXML}
  <ccs2012>
    <concept>
      <concept_id>10010147.10010257.10010293.10011809.10011812</concept_id>
      <concept_desc>Computing methodologies~Genetic algorithms</concept_desc>
      <concept_significance>500</concept_significance>
    </concept>
    <concept>
      <concept_id>10010147.10010257</concept_id>
      <concept_desc>Computing methodologies~Machine learning</concept_desc>
      <concept_significance>300</concept_significance>
    </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Genetic algorithms}
\ccsdesc[300]{Computing methodologies~Machine learning}

\keywords{genetic algorithm, machine learning, parameter space}

\maketitle

\input{body}

\begin{acks}
  \footnotesize
  \linespread{0.5}
  This research was supported by a grant [KCG-01-2017-05] through the Disaster and Safety Management Institute funded by Korea Coast Guard of Korean government. This research was also supported by the MIST (Ministry of Science and ICT), Korea, under the National Program for Excellence in SW supervised by the IITP (Institute for Information \& communications Technology Promotion)(2017-0-00096).
  \par
\end{acks}

\bibliographystyle{ieeetr}
\bibliography{bibliography}

\end{document}
